\section{Introduction}
\Glspl{game} premised on \gls{graph} \glspl{algorithm} have always been played as a pastime. Mostly without the knowledge about the underlying mathematical theories, which are -- of course -- not always relevant for clearing \gls{level} after level. While two humans playing a graph game usually agree on the eventuation of one player winning the game, the same game on a computer must be computed to declare one \gls{player} the winner.\par

This is where \graphioli takes effect. The \Gls{java} \gls{framework} simplifies the process of developing graph-based computer games by providing a straightforward, intuitive \gls{library} that allows its user to focus the effort to the game's logical implementation. Recurring and redundant operations, algorithms and codings will be taken care of by \graphioli.\par

The framework still does not release the \gls{developer} from actual programming work. However, it reduces the amount of time formerly spent realizing graphical outputs, structures and user interactions, thus reinventing the wheel.\par

Products based on \graphioli will be well-structured, lightweight in terms of code size and easy to maintain.\par

\subsection{How to read this document}\label{REF:HOW-TO-READ}

In this \emph{Functional Specification Document} it is the talk of \glspl{customer}, \glspl{user}, \glspl{developer} and \glspl{player}. The customer of this product, the \graphioli framework, is the \emph{developer}. Someone who needs a library to implement his or her ideas of graph-based \glspl{game}.\par
The user who afterwards executes the program containing this implemented game is then referred to as the \emph{player}.