\subsection{Mandatory criteria}\label{REF:MANDATORY-CRITERIA}
\subsubsection{Framework}
\begin{itemize}

	\item The framework provides rudimental functions that either all or the most \glspl{game} need:
	\begin{itemize}
		\item Creation of new \glspl{graph} from specifications,
		\item manipulation of existing graphs (removing or adding edges or vertices, changing style) and 
		\item visualization of these graphs.
	\end{itemize}

	\item These graphs consist of \glspl{edge} and \glspl{vertex} that themselves are equipped with attributes. For vertices these are
	\begin{itemize}
		\item background icon,
		\item background color,
		\item stroke weight,
		\item stroke color,
		\item size,
		\item coordinates and
		\item a unique \gls{ID}.
	\end{itemize}
	Parameters that are related to edges are
	\begin{itemize}
		\item weight,
		\item color,
		\item width and
		\item direction.
	\end{itemize}
	These parameters can change during the course of the game (due to user action or game logic).

	\item The framework comes with default parameters for edges and vertices. The developer can define own default sets of parameters. E.g considering the subsequently explained {\twixt}, a developer would define a default set A for edges and vertices of the first player and a default set B for the second player.

	\item A \gls{developer} using {\graphioli} does not need to implement a \gls{GUI} for his or her game, because the framework provides all necessary utilities to listen for events, interact, print out statuses and display the graph.

	\item The graph is placed in a predefined grid system. The developer specifies the size, respectively the granularity of the grid.

	\item The framework lightens the developer's workload by providing access to the reoccuring basic graph and \gls{path} finding algorithms:
	\begin{itemize}
		\item \gls{BFS},
		\item \gls{DFS},
		\item an algorithm for finding direct or indirect connections between vertices,
		\item an algorithm for verifying \gls{planarity} and
		\item the functionality to check for crossing edges\todo{List all algorithms here}.
	\end{itemize}

	\item {\graphioli} will offer interfaces for creating multiplayer modes so that two or more \glspl{player} are able to play against each other on the same computer sharing the same peripherals.

	\item Games can be saved and reloaded by their player at a later time without losing \gls{level} stats.

	\item In order to facilitate easy implementations, {\graphioli} comes with elaborate \Gls{javadoc} documentation from the viewpoint of the developer using the framework.

\end{itemize}

\subsubsection{GUI}
\paragraph*{Game window}
When a game is selected for playing, the game window opens. It shows a canvas containing the graph (or an empty area), the menu bar and the status bar.
\paragraph*{Game-Explorer}
The Game-Explorer is a graphical interface that builds the main contact point with the framework for a \gls{player}. Without knowledge about the background of framework and implemented \gls{game} logic, the player is still able to start and restart games from a list of available or previously saved games and switch between singleplayer and multiplayer mode (if provided in the selected game).\par
For that reason, the Game-Explorer can display information to every game: the title, a description, a static screenshot and a detailed help file.\par

\subsubsection{Games}
{\graphioli} comes with two already implemented games.\par
\paragraph*{\twixt}
The two-player strategy board game {\twixt} is one of the most popular graph games. Both players have their own color that they use to colorize the vertices by turns in a 24x24 grid. Each player owns one of the two pairs of opposite border rows. Their contrary objective is to build a continuous \gls{path} of linked vertices connecting their border rows.\par
Two vertices can be linked by an edge, if they share a knight's move distance to each other. Since edges are not allowed to cross, a player can try to interfere the other in accomplishing this objective by blocking his or her way.\par
If both sides cannot achieve such a path, the game is a draw.\par
Invented by board game designer \emph{Alexander Randolph} in the early 60s, {\twixt} has since been awarded several prizes, including nomination for \emph{Spiel des Jahres} in 1979\footnote{For more information see official page of \emph{Spiel des Jahres}: \url{http://www.spiel-des-jahres.com/cms/front_content.php?idcatart=474&id=370} (in German)}.\par
\paragraph*{\graphcoloring}
The second game is a game variant of {\graphcoloring} in which the player (or players) tries to colorize the vertices of a graph in such a way that two \gls{adjacent} vertices never get the same color. The player is, depending on the level, restricted in the number of different colors that can be used and the number of \gls{undo} steps that he or she can perform.\par
In multiplayer mode, one players tries to block the other from achieving a fully colored graph. The player who performs the last legal draw wins.\par
A popular use case of the theory behind {\graphcoloring} is the smallest set of colors needed to colorize a map of neighboring countries (which is indeed a set containing a maximum of four colors, see \emph{\gls{four-color-theorem}}).\todo{Was ist hier falsch? Es geht ja nur um Länder auf Karten (euklidische Ebene).}\par