\section{Introduction}
\Glspl{game} premised on \gls{graph} \glspl{algorithm} have always been played as a pastime. Mostly without the knowledge about the underlying mathematical theories, which are -- of course -- not always relevant for clearing \gls{level} after level. While two humans playing a graph game usually agree on the eventuation of one player winning the game, the same game on a computer must be computed to declare one \gls{player} the winner.\par

This is where \graphioli takes effect. The \Gls{java} \gls{framework} simplifies the process of developing graph-based computer games by providing a straightforward, intuitive \gls{library} that allows its user to focus the effort to the game's logical implementation. Recurring and redundant operations, algorithms and codings will be taken care of by \graphioli.\par

The framework still does not release the \gls{developer} from actual programming work. However, it reduces the amount of time formerly spent realizing graphical outputs, structures and user interactions, thus reinventing the wheel.\par

Products based on \graphioli will be well-structured, lightweight in terms of code size and easy to maintain.\par

\subsection{About this document}

This \emph{Software Design Document} intends to inform about design decisions and provide insights into inter-class dependencies, sequences of program interactions and the consequences of specific method calls.\par
Thus, the document supplies the reader with \gls{UML} based sequence, class and architecture diagrams and describes every implemented class and method.